Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
review introduction
reviewed related work

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. \textcolor{red}{In the second approach,...}

@@

\addtodo{Add contributions (Cristina)}

@@

Program synthesis is the problem of computing correct-by-design programs
from high-level specifications, and algorithms for this problem have made
substantial progress in recent years.  One such
approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
generate the desired programs.

Program synthesisers are an ideal fit for synthesis of parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesize.
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesizing continuous-time switching
controllers that guarantee reach while stay properties of a closed
loop system. The solution is based on synthesizing control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

>>>>

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. \textcolor{red}{Dario: Can you please briefly explain your approach?
In the second approach,...}

@@

\addtodo{We have to summarize our main contributions here}

@@

Program synthesis is the problem of computing correct-by-design programs
from high-level specifications; algorithms for this problem have made
substantial progress in recent years.  One such
approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
generate the desired programs.

Program synthesisers are an ideal fit for synthesis of parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesize.
\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesizing continuous-time switching
controllers that guarantee reach while stay properties of a closed
loop system}. The solution is based on synthesizing control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.
